\documentclass[12pt]{article}
\usepackage{pmmeta}
\pmcanonicalname{Ideal}
\pmcreated{2013-03-22 11:49:27}
\pmmodified{2013-03-22 11:49:27}
\pmowner{djao}{24}
\pmmodifier{djao}{24}
\pmtitle{ideal}
\pmrecord{18}{30371}
\pmprivacy{1}
\pmauthor{djao}{24}
\pmtype{Definition}
\pmcomment{trigger rebuild}
\pmclassification{msc}{14K99}
\pmclassification{msc}{16D25}
\pmclassification{msc}{11N80}
\pmclassification{msc}{13A15}
\pmclassification{msc}{54C05}
\pmclassification{msc}{54C08}
\pmclassification{msc}{54J05}
\pmclassification{msc}{54D99}
\pmclassification{msc}{54E05}
\pmclassification{msc}{54E15}
\pmclassification{msc}{54E17}
\pmrelated{Subring}
\pmrelated{PrimeIdeal}
\pmdefines{left ideal}
\pmdefines{right ideal}
\pmdefines{2-sided ideal}
\pmdefines{two-sided ideal}

\endmetadata

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
%%%%\usepackage{xypic}
\begin{document}
\PMlinkescapeword{term}
Let $R$ be a ring. A \emph{left ideal} (resp., \emph{right ideal}) $I$ of $R$ is a nonempty subset $I \subset R$ such that:
\begin{itemize}
\item $a-b \in I$ for all $a,b \in I$
\item $r \cdot a \in I$ (resp. $a \cdot r \in I$) for all $a \in I$ and $r \in R$
\end{itemize}
A \emph{two-sided ideal} is a left ideal $I$ which is also a right ideal. If $R$ is a commutative ring, then these three notions of ideal are equivalent. Usually, the word ``ideal'' by itself means two-sided ideal.

The name ``ideal'' comes from the study of number theory.  When the failure of unique factorization in number fields was first noticed, one of the solutions was to work with so-called ``ideal numbers'' in which unique factorization did hold.  These ``ideal numbers'' were in fact ideals, and in Dedekind domains, unique factorization of ideals does indeed hold.  The term ``ideal number'' is no longer used; the term ``ideal'' has replaced and generalized it.
%%%%%
%%%%%
%%%%%
%%%%%
\end{document}
